---
title: "R - Introduction"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Índice
1. [print()](#print)
1. [Comments #](#comments)

[Índice](#índice)

## print

To output text we use the method `print()`. It works same as in Python.

```{r}
print("Hello, world")
```

---

[Índice](#índice)

## Comments

To use comments we use the character "#"

```{r}
# Outputs "Hello, world"
print("Hello, world")
```

---

[Índice](#índice)

## Variables

In R the variable type does not have to be defined.

However if we want to store as an integer we put the character "L" next to the value of the variable.

We can use `=`, `->` or `<-` to assign a value to a variable

```{r}
x = 42L
y = 42
z = 'hola'
print(typeof(x))
print(typeof(y))
print(typeof(z))

```

---

[Índice](#índice)

## cat

To output text we can also use the cat() method.

This help us to concatenate
```{r}
z = 'hola \"Santiago\"'
print(z)
```

```{r}
x = 10
z = 'hola \"Santiago\"'
cat(z, x)
```

---

[Índice](#índice)

## Math

- Exponentiation we use "**" or "^"
- Module "%%" 
- Integer division "%/%".
- min()
- max()
- sqrt()


---

[Índice](#índice)


## Booleans

There are two boolean values in R: `TRUE` and `FALSE`.

The logic operators are:

- Greater >
- <
- <=
- >=
- ==
- !=

---

[Índice](#índice)


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
